### 2023-03-08 output/summary_statistics/tables/summary_statistics.tex

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{2}{4cm}{\textit{Panel A: Pre-treatment Zestimates}} & Change, Jan. 2017 to Jan. 2019 & 46,593.74 & 37,330.00 & 158,125.14 & 10,160 \\
 & Zestimate, Jan. 2017 & 298,908.73 & 235,117.00 & 352,754.39 & 10,176 \\
\cline{1-6}
\multirow[c]{7}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,797.07 & 1,355.40 & 17,579.99 & 40,726 \\
 & Median household income (2016) & 52,659.44 & 47,105.00 & 27,177.48 & 40,726 \\
 & Population density (2010) & 9,159.77 & 5,978.61 & 9,574.14 & 40,726 \\
 & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,726 \\
 & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,726 \\
 & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,726 \\
 & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,726 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,727 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,727 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,727 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,727 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,727 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,727 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,727 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,727 \\
 & Case duration & 57.81 & 21.00 & 78.29 & 39,087 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,727 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,727 \\
 & Money judgment & 1,890.34 & 0.00 & 5,279.49 & 40,727 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 377,384.02 & 305,144.00 & 316,645.29 & 10,096 \\
 & One year after filing date & 421,601.75 & 347,550.00 & 344,328.86 & 10,443 \\
 & Three years after filing date & 501,611.80 & 414,600.00 & 780,467.01 & 5,894 \\
 & Two years after filing date & 477,948.08 & 393,900.00 & 457,694.83 & 9,175 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & Mean & Median & S.D. & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{14}{4cm}{\textit{Panel A: Pre-treatment Outcomes}} & Zestimate, Jan. 2017 & 298,898.22 & 235,078.00 & 352,756.46 & 10,176 \\
 & pre_treatment_change_in_any_crime_140m & 0.02 & 0.00 & 2.42 & 40,734 \\
 & pre_treatment_change_in_any_crime_200m & 0.05 & 0.00 & 3.31 & 40,734 \\
 & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
 & pre_treatment_change_in_any_crime_60m & 0.01 & 0.00 & 1.16 & 40,734 \\
 & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
 & pre_treatment_change_in_any_crime_90m & 0.03 & 0.00 & 1.71 & 40,734 \\
 & pre_treatment_change_in_zestimate & 46,593.08 & 37,330.00 & 158,125.24 & 10,160 \\
 & twenty_seventeen_any_crime_140m & 1.41 & 0.00 & 5.01 & 40,734 \\
 & twenty_seventeen_any_crime_200m & 2.68 & 0.00 & 8.69 & 40,734 \\
 & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
 & twenty_seventeen_any_crime_60m & 0.29 & 0.00 & 1.31 & 40,734 \\
 & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
 & twenty_seventeen_any_crime_90m & 0.62 & 0.00 & 2.42 & 40,734 \\
\cline{1-6}
\multirow[c]{8}{4cm}{\textit{Panel B: Census Tract Characteristics}} & Jobs per square mile (2010) & 4,802.71 & 1,355.40 & 17,583.20 & 40,732 \\
 & Median household income (2016) & 52,695.02 & 47,105.00 & 27,212.35 & 40,732 \\
 & Median two bedroom rent (2015) & 1,116.73 & 1,055.00 & 396.69 & 30,546 \\
 & Population density (2010) & 9,151.92 & 5,982.68 & 9,537.28 & 40,732 \\
 & Share below poverty line & 0.20 & 0.16 & 0.15 & 40,732 \\
 & Share white (2010) & 0.58 & 0.63 & 0.29 & 40,732 \\
 & Share with bachelor's degree & 0.26 & 0.22 & 0.17 & 40,732 \\
 & Share with commute $<$15 minutes (2010) & 0.28 & 0.27 & 0.11 & 40,732 \\
\cline{1-6}
\multirow[c]{3}{4cm}{\textit{Panel C: Case Initiation}} & For cause & 0.12 & 0.00 & 0.33 & 40,734 \\
 & No cause & 0.11 & 0.00 & 0.31 & 40,734 \\
 & Non-payment of rent & 0.75 & 1.00 & 0.43 & 40,734 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.09 & 0.00 & 0.28 & 40,734 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.08 & 40,734 \\
 & Plaintiff has an attorney & 0.84 & 1.00 & 0.37 & 40,734 \\
 & Plaintiff is an entity & 0.70 & 1.00 & 0.46 & 40,734 \\
\cline{1-6}
\multirow[c]{6}{4cm}{\textit{Panel E: Case Resolution}} & Case defaulted & 0.20 & 0.00 & 0.40 & 40,734 \\
 & Case dismised & 0.29 & 0.00 & 0.45 & 40,734 \\
 & Case duration & 57.81 & 21.00 & 78.28 & 39,094 \\
 & Case heard & 0.06 & 0.00 & 0.23 & 40,734 \\
 & Case mediated & 0.41 & 0.00 & 0.49 & 40,734 \\
 & Money judgment & 1,890.02 & 0.00 & 5,279.08 & 40,734 \\
\cline{1-6}
\multirow[c]{14}{4cm}{\textit{Panel F: Post-treatment Outcomes}} & Zestimate one year after filing date & 421,590.21 & 347,444.00 & 344,333.24 & 10,443 \\
 & Zestimate two years after filing date & 477,931.84 & 393,800.00 & 457,699.06 & 9,175 \\
 & any_crime_140m_1_years_relative_to_treatment & 1.41 & 0.00 & 4.90 & 40,734 \\
 & any_crime_140m_2_years_relative_to_treatment & 1.50 & 0.00 & 5.04 & 35,684 \\
 & any_crime_200m_1_years_relative_to_treatment & 2.65 & 0.00 & 8.37 & 40,734 \\
 & any_crime_200m_2_years_relative_to_treatment & 2.84 & 0.00 & 8.74 & 35,684 \\
 & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
 & any_crime_60m_1_years_relative_to_treatment & 0.31 & 0.00 & 1.41 & 40,734 \\
 & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
 & any_crime_60m_2_years_relative_to_treatment & 0.34 & 0.00 & 1.44 & 35,684 \\
 & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
 & any_crime_90m_1_years_relative_to_treatment & 0.66 & 0.00 & 2.50 & 40,734 \\
 & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
 & any_crime_90m_2_years_relative_to_treatment & 0.69 & 0.00 & 2.53 & 35,684 \\
\cline{1-6}
\bottomrule
\end{tabular}
